### 2019-07-01 submission/manuscript.Rmd
Developing outline

Big points: identify the big problems, rate limiting steps, things that were just done wrong
* We may look back and shutter at how things were done, but we need some historical context
* If we solved all of the problems we would never publish or move the field forward
* The most important problem is answering your biological question
* Connect to Lenski's retrospective article

>>>>

Big points: identify the big problems, rate limiting steps, things that were just done wrong
* We may look back and shutter at how things were done, but we need some historical context
* If we solved all of the problems we would never publish or move the field forward
* The most important problem is answering your biological question
